Software Defect Prediction: Review, Commentary, and Future Work

### 2015-12-15 paper/paper.tex
Added discussion for data sources

But why was Windows Vista chosen? Windows in general is a widely used operating system which contains many lines of code. Windows is also known for being vulnerable without frequent patching and antivirus software. Windows Vista may have been the latest version of Windows at the time of both papers, but Vista is also known as a slow and buggy release. Maybe the authors intended to show that Vista did not contain an unusually high number of bugs compared to other releases, or maybe they just wanted to choose a Microsoft product that was well-known, whether for good or bad.

\section{Data Preprocessing}

>>>>

But why was Windows Vista chosen? Windows in general is a widely used operating system which contains many lines of code. Windows is also known for being vulnerable without frequent patching and antivirus software. Windows Vista may have been the latest version of Windows at the time of both papers, but Vista is also known as a slow and buggy release. Maybe the authors intended to show that Vista did not contain an unusually high number of bugs compared to other releases, or maybe they just wanted to choose a Microsoft product that was well-known, whether for good or bad.
\subsection{Discussion}
Most of the studies we examined used open-source datasets which is in line with previous recommendations (\cite{Catal}, \cite{Vandecruys}). The two papers which used Windows Vista were not proposing a new or improved fault prediction model but were instead analyzing Microsoft's organizational structure to see how it may have affected bug levels. Although the NASA software isn't open source, we think that its datasets are acceptable because of their domain and the fact that NASA has made the datasets public for research purposes. Research has heeded the recommendations of earlier researchers and now primarily use open-source datasets
\section{Data Preprocessing}
